\section{Leadership and Extracurricular Activities}

\cventry{July 2023 - July 2023}{\href{https://diversity.cis.cornell.edu/programs/sonic/}{Cornell University - SoNIC Summer Research Workshop}}{Scholar}{}{}{
    Advisor: \href{https://sites.google.com/site/tapomayukh}{Dr. Tapomayukh Bhattacharjee}
\begin{itemize}
\item Worked in groups on building a smart assistive cane for individuals with visual impairments
\item Implemented perception, motion planning, and control for the robot
\item Ranked 2nd in individual final test among 40 participants
\end{itemize}}

\cventry{Mar. 2024 - Present}{Iranian Students Culrual Association of Tucson}{Director and Treasurer}{}{}{
\begin{itemize}
\item Hosted cultural events (e.g. Nowruz, Yalda, etc) in Tucson with over 300 attendees
\item Raised over \$10,000 in donations for the association
\item Managed the association's budget and financial transactions
\end{itemize}}


\cventry{Jan. 2024 - Present}{UofA - Computer Science Department}{Computer Science Ambassador}{}{}{
\begin{itemize}
\item Represented the department at various promotional events and high school visits
\item Led group discussions and presentations at educational outreach events
\end{itemize}}

\cventry{Aug. 2023 - Present}{UofA - Computer Science Department}{Peer Mentor}{}{}{
\begin{itemize}
\item Guided first-year students with their transition to college
\item Helped students in academic and research directions
\item Organized information sessions on course selection and sharing experiences
\end{itemize}}

\cventry{Aug. 2023 - Present}{Google Developer Student Club - UofA}{Vice Lead}{}{}{
\begin{itemize}
\item Revitalized the chapter, growing active participation from 15 to over 70 members
\item Hosted workshops for enhancing club members’ proficiency in ML and NLP frameworks
\end{itemize}}

\cventry{Jan. 2024 - May. 2024}{Apple Pathways Alliance}{Participant}{}{}{
\begin{itemize}
\item Nominated by the department as one of the three students to participate in this program
\end{itemize}}

\cventry{Oct. 2023 - Mar. 2024}{UofA Campus Pantry}{Student Volunteer}{}{}{
\begin{itemize}
\item Volunteered two hours weekly, aiding in food distribution
\end{itemize}}

