\section{Publications}

\cvitem{2025 \\ \textbf{ACL} \\ Findings}{\textbf{MohammadHossein Rezaei*}, Yicheng Fu*, Phil Cuvin*, Caleb Ziems, Yanzhe Zhang, Hao Zhu, and Diyi Yang. 2025. \href{https://arxiv.org/abs/2502.20490}{\textcolor{mygreen}{EgoNormia: Benchmarking Physical Social Norm Understanding}}. In \textit{Findings of the Association for Computational Linguistics: ACL 2025}, Vienna, Austria. Association for Computational Linguistics. \textit{Accepted, to appear}.}
\cvitem{2025 \\ \textbf{NAACL} \\ \tiny{23\% Accept. Rate}}{\textbf{MohammadHossein Rezaei} and Eduardo Blanco. 2025. \href{https://aclanthology.org/2025.naacl-long.413/}{\textcolor{mygreen}{Making Language Models Robust Against Negation}}. In \textit{Proceedings of the 2025 Conference of the Nations of the Americas Chapter of the Association for Computational Linguistics: Human Language Technologies (Volume 1: Long Papers)}, pages 8123–8142, Albuquerque, New Mexico. Association for Computational Linguistics.}
\cvitem{2024 \\ \textbf{ACL} \\ \tiny{21\% Accept. Rate}}{\textbf{MohammadHossein Rezaei} and Eduardo Blanco. 2024. \href{https://aclanthology.org/2024.acl-short.55/}{\textcolor{mygreen}{Paraphrasing in Affirmative Terms Improves Negation Understanding}}. In \textit{Proceedings of the 62nd Annual Meeting of the Association for Computational Linguistics (Volume 2: Short Papers)}, pages 602-615, Bangkok, Thailand. Association for Computational Linguistics.}
\cvitem{2024 \\ \textbf{SemEval} \\ Workshop}{\textbf{MohammadHossein Rezaei}, Yeaeun Kwon, Reza Sanayei, Abhyuday Singh, and Steven Bethard. 2024. \href{https://aclanthology.org/2024.semeval-1.215/}{\textcolor{mygreen}{Clulab-uofa at semeval-2024 task 8: Detecting machine-generated text using triplet-loss-trained text similarity and text classification.}} In \textit{Proceedings of the 18th International Workshop on Semantic Evaluation (SemEval-2024)}, pages 1509-1515, Mexico City, Mexico. Association for Computational Linguistics.}
\cvitem{2024 \\ \textbf{SemEval} \\ Workshop}{Reza Sanayei, Abhyuday Singh, \textbf{MohammadHossein Rezaei}, and Steven Bethard. 2024. \href{https://aclanthology.org/2024.semeval-1.225/}{\textcolor{mygreen}{MARiA at SemEval-2024 Task 6: Hallucination Detection Through LLMs and MNLI and and Cosine similarity.}} In \textit{Proceedings of the 18th International Workshop on Semantic Evaluation (SemEval-2024)}, Mexico City, Mexico. Association for Computational Linguistics.}
\cvitem{2023 \\ \textbf{EMNLP} \\ Findings \\ \tiny{43\% Accept. Rate}}{Zijie Wang, Md Hossain, Shivam Mathur, Terry Melo, Kadir Ozler, Keun Park, Jacob Quintero, \textbf{MohammadHossein Rezaei}, Shreya Shakya, Md Uddin, and Eduardo Blanco. 2023. \href{https://aclanthology.org/2023.findings-emnlp.146/}{\textcolor{mygreen}{Interpreting Indirect Answers to Yes-No Questions in Multiple Languages}}. In \textit{Findings of the Association for Computational Linguistics: EMNLP 2023}, pages 2210-2227, Singapore. Association for Computational Linguistics.}
\cvitem{2022 \\ \tiny{Highschool Publication}}{\textbf{Rezaei, M.}. (2022). \href{https://www.awesomemath.org/wp-pdf-files/math-reflections/mr-2022-03/mr\_3\_2022\_solving\_functional\_equations\_in\_r+.pdf}{\textcolor{mygreen}{Solving Functional Equations in $R^+$ Using Inequalities and Sequences}}. \textit{Mathematical Reflections}, 2022(3), 1-4.}
  