\section{Computer Science Courses}


\cventry
{A \\ \small{\textit{3.0 Units}}}
{CSc 585 -  Algorithms for NLP}
{Fall 2024}
{}
{}
{
  \begin{itemize}
    \item \texttt{Instructor:} \href{https://eduardoblanco.github.io/}{Eduardo Blanco}
    \item \texttt{Final Grade:} Grades available \href{https://mhrezaei.com/assets/cv/courses/Fall2024/CSC585/Grades.pdf}{here}.
    \item \texttt{Syllabus:} \href{https://mhrezaei.com/assets/cv/courses/Fall2024/CSC585/Syllabus.pdf}{Available here}.
    \item \texttt{Programming Language:} Python (PyTorch, TensorFlow, spaCy, NLTK).
    \item \texttt{Summary of Topics:} This course covers important algorithms for natural language processing (NLP), including
    traditional NLP algorithms, distributional similarity algorithms such as word embeddings,
    sequence labeling models, neural networks such as recurrent, recursive and convolutional neural
    networks, transformers, and parsing algorithms such as shift-reduce. The course will focus on
    the algorithms that underlie NLP rather than the application of NLP to various problem domains.
    We will cover syntax, semantics, and pragmatics. Topics will include both classical and cutting-
    edge algorithms.
  \end{itemize}
}

\cventry
{A \\ \small{\textit{3.0 Units}}}
{CSc 352 - Systems Programming and UNIX}
{Fall 2024}
{}
{}
{
  \begin{itemize}
    \item \texttt{Instructor:} \href{https://www.cs.arizona.edu/person/eric-anson}{Eric Anson}
    \item \texttt{Final Grade:} 94.41\%. Grades available \href{https://mhrezaei.com/assets/cv/courses/Fall2024/CSC352/Grades.pdf}{here}.
    \item \texttt{Syllabus:} \href{https://mhrezaei.com/assets/cv/courses/Fall2024/CSC352/Syllabus.pdf}{Available here}.
    \item \texttt{Programming Language:} C.
    \item \texttt{Summary of Topics:} Programming in C, including arrays, lists, stacks, queues, trees, pointers, and dynamic
    memory allocation. Unix topics, including debuggers, makefiles, shell programming, and other topics that support
    C programming.
  \end{itemize}
}



\cventry
{A \\ \small{\textit{3.0 Units}}}
{CSc 345 - Analysis of Discrete Structures}
{Fall 2024}
{}
{}
{
  \begin{itemize}
    \item \texttt{Instructor:} \href{http://mccann.cs.arizona.edu}{Lester I. McCann, Ph.D.}
    \item \texttt{Final Grade:} 94.90\%. Grades available \href{https://mhrezaei.com/assets/cv/courses/Fall2024/CSC345/Grades.pdf}{here}.
    \item \texttt{Syllabus:} \href{https://mhrezaei.com/assets/cv/courses/Fall2024/CSC345/Syllabus.pdf}{Available here}.
    \item \texttt{Programming Language:} Java.
    \item \texttt{Textbook:} \href{https://people.cs.vt.edu/shaffer/Book/JAVA3elatest.pdf}{Data Structures and Algorithm Analysis, by Clifford Shaffer, 2013}.
    \item \texttt{Summary of Topics:} Introduction to and analysis of algorithms and characteristics of discrete structures. Course
    topics include algorithm analysis techniques, recurrence relations, structural induction,
    hierarchical structures, graphs, hashing, and sorting.
  \end{itemize}
}


\cventry
{P \\ \small{\textit{1.0 Units}}}
{CSc 493 - Internship}
{Summer 2024}
{}
{}
{
  \begin{itemize}
    \item \texttt{Credit Earned:} Internship at Stanford University as an visiting research intern.
  \end{itemize}
}

\cventry
{S \\ \small{\textit{3.0 Units}}}
{CSc 492 - Directed Research}
{Spring 2024}
{}
{}
{
  \begin{itemize}
    \item \texttt{Credit Earned:} Undergraduate research assistant for \href{https://bethard.github.io/}{Dr. Steven Bethard}.
  \end{itemize}
}

\cventry
{S \\ \small{\textit{3.0 Units}}}
{CSc 391 - Preceptorship}
{Spring 2024}
{}
{}
{
  \begin{itemize}
    \item \texttt{Credit Earned:} Undergraduate teaching assistant for \href{https://mccann.cs.arizona.edu/}{Dr. Lester McCann} in \href{https://www2.cs.arizona.edu/classes/cs144/fall23-002/}{CSc 144}.
    \item \texttt{Course Description:} Available \href{https://mhrezaei.com/assets/cv/courses/Fall2023/CSC391/Syllabus.pdf}{here}.
  \end{itemize}
}

\cventry
{A \\ \small{\textit{3.0 Units}}}
{CSc 335 - Object-Oriented Programming and Design}
{Spring 2024}
{}
{}
{
  \begin{itemize}
    \item \texttt{Instructor:} \href{https://www2.cs.arizona.edu/~mercer/}{Rick Mercer}
    \item \texttt{Final Grade:} 98.95\%. Grades available \href{https://mhrezaei.com/assets/cv/courses/Spring2024/CSC335/Grades.pdf}{here}.
    \item \texttt{Programming Language:} Java.
    \item \texttt{Summary of Topics:} Fundamentals of object-oriented software development. Includes design principles, inheritance, polymorphism, Unified Modeling Language (UML), testing, event-driven programming with graphical user interfaces, applications of design patterns, and use of existing frameworks.
  \end{itemize}
}


\cventry
{A \\ \small{\textit{3.0 Units}}}
{CSc 252 - Computer Organization}
{Spring 2024}
{}
{}
{
  \begin{itemize}
    \item \texttt{Instructor:} \href{https://www.cs.arizona.edu/person/russell-lewis}{Russell Lewis}
    \item \texttt{Final Grade:} 96.48\%. Grades available \href{https://mhrezaei.com/assets/cv/courses/Spring2024/CSC252/Grades.pdf}{here}.
    \item \texttt{Programming Language:} C, Java, MIPS Assembly.
    \item \texttt{Summary of Topics:} Basic machine organization; elementary hardware concepts; interrupts. Machine operations and instructions; assembly language concepts and programming.
  \end{itemize}
}

\cventry
{A \\ \small{\textit{3.0 Units}}}
{CSc 337 - Web Programming}
{Fall 2023}
{}
{}
{
  \begin{itemize}
    \item \texttt{Instructor:} \href{https://benjdd.com/}{Benjamin Dicken}
    \item \texttt{Final Grade:} 97.77\%. Grades available \href{https://mhrezaei.com/assets/cv/courses/Fall2023/CSC337/Grades.pdf}{here}.
    \item \texttt{Syllabus:} \href{https://mhrezaei.com/assets/cv/courses/Fall2023/CSC337/Syllabus.pdf}{Available here}.
    \item \texttt{Programming Language:} JavaScript.
    \item \texttt{Final Project:} A specialized room reservation system for the Computer Science Department at the University of Arizona, to be used starting Spring 2025.
    \item \texttt{Summary of Topics:} HTML, CSS, JavaScript, DOM, Event-Driven Programming, NodeJS, AJAX and Promises, Express, MongoDB, Mongoose, JSON, Web Security, Sessions, Cookies, MERN, and React.
  \end{itemize}
}

\cventry
{A \\ \small{\textit{3.0 Units}}}
{CSc 244 - Discrete Math for Computer Science II}
{Fall 2023}
{}
{}
{
  \begin{itemize}
    \item \texttt{Instructor:} \href{https://www.cs.arizona.edu/person/reyan-ahmed}{Reyan Ahmed, Ph.D.}
    \item \texttt{Final Grade:} 104.49\% with extra credits. Grades available \href{https://mhrezaei.com/assets/cv/courses/Fall2023/CSC244/Grades.pdf}{here}.
    \item \texttt{Syllabus:} \href{https://mhrezaei.com/assets/cv/courses/Fall2023/CSC244/Syllabus.pdf}{Available here}.
    \item \texttt{Textbook:} \href{https://www.mheducation.com/highered/product/M125967651X.html}{Discrete Mathematics and Its Applications, 8th Edition by Kenneth Rosen}.
    \item \texttt{Summary of Topics:} The Pigeonhole Principle, Proofs, Recurrence Relations, Induction \& Recursion, Graphs \& Graph Models, Representing Graphs \& Graph Isomorphism, Connectivity, Euler \& Hamilton Paths, Trees, Languages \& Grammars, Finite-State Machines with Output, Finite-State Machines with No Output, Language Recognition, and Turing Machines.
  \end{itemize}
}

\cventry
{A \\ \small{\textit{4.0 Units}}}
{CSc 210 - Software Development}
{Fall 2023}
{}
{}
{
  \begin{itemize}
    \item \texttt{Instructor:} \href{https://www.cs.arizona.edu/person/rick-mercer}{Rick Mercer}
    \item \texttt{Final Grade:} 98.05\%. Grades available \href{https://mhrezaei.com/assets/cv/courses/Fall2023/CSC210/Grades.pdf}{here}.
    \item \texttt{Syllabus:} \href{https://mhrezaei.com/assets/cv/courses/Fall2023/CSC210/Syllabus.pdf}{Available here}.
    \item \texttt{Programming Language:} Java.
    \item \texttt{Textbook:} \href{https://www.lulu.com/shop/rick-mercer/computing-fundamentals-with-java-and-junit/paperback/product-23373195.html?page=1&pageSize=4}{Computing Fundamentals with Java and JUnit, Rick Mercer, Paaz Publishing}.
    \item \texttt{Summary of Topics:} Java Fundamentals, Objects and Classes, String Objects, Java Methods/Parameters, Arrays, File I/O, For Loops, While Loops, Exception Handling, Generics with <Type> Arguments, Java.util.HashMap, Binary Trees, Binary Search Trees (BSTs), Recursion, Git, and GitHub.
  \end{itemize}
}

\cventry
{S \\ \small{\textit{3.0 Units}}}
{CSc 391 - Preceptorship}
{Fall 2022}
{}
{}
{
  \begin{itemize}
    \item \texttt{Credit Earned:} Undergraduate teaching assistant for \href{https://mccann.cs.arizona.edu/}{Dr. Lester McCann} in \href{https://www2.cs.arizona.edu/classes/cs144/fall23-002/}{CSc 144 - Discrete Math for Computer Science I}.
    \item \texttt{Course Description:} Available \href{https://mhrezaei.com/assets/cv/courses/Fall2023/CSC391/Syllabus.pdf}{here}.
  \end{itemize}
}

\cventry
{A \\ \small{\textit{3.0 Units}}}
{CSc 144 - Discrete Math for Computer Science I}
{Spring 2023}
{}
{}
{
  \begin{itemize}
    \item \texttt{Instructor:} \href{http://mccann.cs.arizona.edu}{Lester I. McCann, Ph.D.}
    \item \texttt{Ranked:} \textit{Fourth} among ~250 students. Ranking's list available \href{https://mhrezaei.com/assets/cv/courses/Spring2023/CSC144/Rankings.pdf}{here}, identifier: 974718.
    \item \texttt{Final Grade:} 96.99\%. Grades available \href{https://mhrezaei.com/assets/cv/courses/Spring2023/CSC144/Grades.pdf}{here}.
    \item \texttt{Syllabus:} \href{https://mhrezaei.com/assets/cv/courses/Spring2023/CSC144/Syllabus.pdf}{Available here}.
    \item \texttt{Programming Language:} Prolog.
    \item \texttt{Textbook:} \href{https://www.mheducation.com/highered/product/M125967651X.html}{Discrete Mathematics and Its Applications, 8th Edition by Kenneth Rosen}.
    \item \texttt{Summary of Topics:} Logic, Quantifiers, Arguments, Direct Proofs, Set Concepts, Relations, Functions, Indirect Proofs, Integers, Sequences and Strings, Methods of Counting, and Finite Probability.
  \end{itemize}
}

\cventry
{A \\ \small{\textit{4.0 Units}}}
{CSc 120 - Introduction to Computer Programming II}
{Spring 2023}
{}
{}
{
  \begin{itemize}
    \item \texttt{Instructor:} \href{https://cs.arizona.edu/person/janalee-obagy-0}{Janalee O'Bagy, Ph.D.}
    \item \texttt{Final Grade:} 95.37\%. Grades available \href{https://mhrezaei.com/assets/cv/courses/Spring2023/CSC120/Grades.pdf}{here}.
    \item \texttt{Syllabus:} \href{https://mhrezaei.com/assets/cv/courses/Spring2023/CSC120/Syllabus.pdf}{Available here}.
    \item \texttt{Programming Language:} Python.
    \item \texttt{Summary of Topics:} Basics of Object-Oriented Programming, References, Linked Lists, Stacks and Queues, Recursion, Trees, Testing, Complexity, Hashing, Debugging, Exceptions, List Comprehensions, and Recursive Search.
  \end{itemize}
}

\cventry
{A \\ \small{\textit{4.0 Units}}}
{CSc 110 - Introduction to Computer Programming I}
{Fall 2022}
{}
{}
{
  \begin{itemize}
    \item \texttt{Instructor:} \href{https://adrianapicoral.com/}{Adriana Picoral, Ph.D.}
    \item \texttt{Grades:} Available \href{https://mhrezaei.com/assets/cv/courses/Fall2022/CSC110/Grades.pdf}{here}.
    \item \texttt{Syllabus:} \href{https://mhrezaei.com/assets/cv/courses/Fall2022/CSC110/Syllabus.pdf}{Available here}.
    \item \texttt{Programming Language:} Python.
    \item \texttt{Summary of Topics:} Python Basics, Strings, Numeric and Variables, Controlling Data Output, If-Elif-Else Statements, Repetition, While-Loops, Loop Table, Functions, Basic Graphical Shapes, Graphical Motion, Lists, For-Loops, Reading and Writing Files, Sets, Dictionaries, Multi-dimensional Data Structures, Tuples, PPM Images, Searching, and Sorting.
  \end{itemize}
}